### 2017-01-20 paper1.tex
Made Christine's revisions

Another approach has been to explicitly model the multiphase ISM
below the resolution limit.  \citet{Springel2003} described a multiphase
model based on the theoretical framework of \citet{McKee1977}.  Each
particle was composed of an isobaric mix of cold clouds and ambient warm
to hot gas.  Radiative cooling coverts warmer gas into cold.  The cold
phase forms stars on a characteristic timescale chosen to yield a
Schmidt-type star formation law.  An empirical model of stellar feedback
evaporates the cold phase.  \citet{Springel2003} recognized that while
this model works well for simulating star formation and feedback in
quiescent galaxies, the coupling of hot and cold mass can prevent hot
gas from leaving the disc as winds or outflows.  Their solution was to
convert a fraction of the feedback energy in a kinetic kick on selected
particles, in the same vein as \citet{Mihos1994}.

@@

Young stellar population steadily release energy in the form of winds and SNe at
a rate of $3\times 10^{38}\;\mathrm{erg\; s^{-1} M_\odot^{-1}}$ for around 40
Myr~\citep{Leitherer1999}. We deposit this energy into the gas particle nearest
to the star particle.  In following with past work, we use the feedback rates
and times for supernovae, but the method is general enough to handle heating
from stellar winds, ionization, etc.  Heating takes effect
$4\;\mathrm{Myr}$ after a star forms, and continues until $30\;\mathrm{Myr}$
after the star particle forms (the time associated with SNII from OB stars).  Thus,
each supernova releases $10^{51}\;\mathrm{erg}$, and each star particle will
release $10^{49}\;\mathrm{erg M^{-1}_\odot}$ using the \citet{Chabrier2003} IMF.

\subsection{Thermal Conduction}
In an ionized gas, thermal conduction, mediated by electrons,
transports heat down temperature gradients.  This flux, $\mathbf{Q} =
-\kappa\nabla T$, depends on the temperature gradient and the conduction
coefficient, as derived by \citet{Cowie1977},
\begin{equation} \label{coefficient1}
    \kappa(T) = 1.8\left(\frac{2}{\pi}\right)^{3/2}\frac{T^{5/2}k_B^{7/2}}{m_e\,e^4\ln\Lambda}.
\end{equation}
This coefficient depends only on the Coulomb logarithm $\ln\Lambda$ (which has
an extremely weak dependence on density), and is well approximated by $\kappa(T)
= \kappa_0\,T^{5/2}$, where $\kappa_0$ is $6.1\times10^{-7}\;\mathrm{erg\;s^{-1}
K^{-7/2}cm^{-1}}$ in the absence of magnetic fields.  In order for this
situation to not cause spontaneous currents, a corresponding mass flux,
{\it in the opposite direction}, must also occur \citep{Cowie1977}.  With
spherical symmetry, this implies a mass flow rate that depends on the sound
speed in the hot gas, $c_{\rm s}$, as follows,
\begin{equation}\label{conservation1}
    \frac{5}{2}\dot M c_{\rm s}^2 = 4\,\pi^2r^2\kappa(T)\frac{{\rm d}T}{{\rm d}r}.
\end{equation}

These rates hold only when the mean free path of electrons in the medium is
smaller than the scale length of the temperature gradient.  If the gradient
becomes steep enough, the heat flux (and corresponding mass flux) saturates at a
value that depends only on the density, temperature, and thermal velocity of the
electrons in the medium \citep{Cowie1977},
\begin{equation}\label{heatflux1}
    \mathbf{Q} = \nabla\left(\frac{3}{2}n_ek_BT_ev_e\right).
\end{equation}
This saturation has the convenient numerical side effect of setting the smallest
timestep required to resolve this mass flux to $\sim 1/17$ the standard Courant
time.

@@

\subsection{Evaporation}
The dominant physical process governing mass flux between the hot and cold
phases of a feedback bubble is thermal conduction between the dense shell and
the hot interior.   As this process takes place on length scales far below the
resolution limit, we must capture its effects in a subgrid model.  For the thin
shell surrounding a feedback bubble, thermal conduction causes an evaporative
mass flux from the cold shell into the hot bubble.  Following
\citet{MacLow1988}, the mass flux into a bubble with interior temperature $T$
is,
\begin{equation}\label{massflux1}
    \frac{{\rm d }M_b}{{\rm d}t} = \frac{4\,\pi\mu}{25k_B}\kappa_0\,\frac{\Delta T^{5/2}}{\Delta x}\ A,
\end{equation}
where $ A$ is the bubble surface area and $\Delta x$ is the thickness of
the hot layer.  For the Smoothed Particle Hydrodynamics (SPH) method used for
our tests, we calculate evaporation using the outer layer of hot particles
bordering the cold gas.  The members of this layer are those with no other hot
particles within $45^o$ of the vector to the centre of mass of their cold
neighbours.  As we cannot directly determine the radius of a well-resolved
superbubble without expensive non-local calculations, we need a way to allow
each particle to estimate the radius and thus its fractional contribution of the
shell surface area.  The total area estimated by all hot particles in a bubble
should approach $\sim 4\pi R^2$ where $R$ is the bubble radius.  For a poorly
resolved bubble $R \sim 1-2\,h$, where $h$ is a hot particle's SPH smoothing
length.  For larger bubbles each hot particle contributes an area of $\sim h^2$
and each particle sees a nearly plane-parallel section of the cold shell.  We
examined a number of bubbles at different stages of growth, as well as a
plane-parallel slab, and empirically found that a good per-particle area
estimate was $A = \frac{6\,\pi\,h^2}{N_{\rm hot}}$, where $N_{\rm
hot}$ is the number of hot neighbours for that particle and $\Delta x = h$.  We
stress that this is a fit for our specific SPH neighbour approach (described
below) that should be recalibrated for other codes.

@@

\begin{equation}\label{multiphase_fractions1}
    m = m_{\rm hot}+m_{\rm cold}\\
    E = u_{\rm hot}m_{\rm hot}+u_{\rm cold}m_{\rm cold}
\end{equation}

Assuming pressure equilibrium, both phases will have the same pressure $P$, and
their densities are found using this and the total density $\rho$:
\begin{equation}\label{multiphase_pressurebalance1}
    \frac{P}{\rho} = \frac{(\gamma-1)E}{m}
\end{equation}
\begin{equation}\label{multiphase_densities1}
    \rho_{\rm cold} = \frac{P}{(\gamma-1)u_{\rm cold}}\\
    \rho_{\rm hot} = \frac{P}{(\gamma-1)u_{\rm hot}}
\end{equation}

@@

We placed a star cluster with mass $3\times10^4\;\mathrm{M_\odot}$ in an uniform
periodic box $2\times2\times2\;\mathrm{kpc}$ in size, containing
$10^3\;\mathrm{K}$ gas with solar metallicity at a density of
$1\;\mathrm{cm^{-3}}$.   This gives a gas particle mass of $760\; M_\odot$,
$6080\; M_\odot$, and $48640\; M_\odot$ for resolutions of $128^3$, $64^3$, and
$32^3$ respectively.  These tests do not include photoheating.

Figure~\ref{onestar_column1} shows the column density projection for the three
different feedback models in an isotropic medium.  injection model.   The hot
interior of the bubble produced using the simple feedback model contains less
mass at $128^3$ than the direct injection model and is subsequently too poorly
resolved for the instabilities formed in the accelerated shell
\citep{Vishniac1983} to mix the bubble and shell through turbulence and
diffusion.

@@

\subsubsection{Clumpy Medium}\label{clumpy1}
As the real ISM is highly inhomogeneous (and as \citet{Silich1996} showed, cold
clumps can also be a source of evaporated cold material) , we ran two additional
simulations with cold, dense clumps with $100\;\mathrm{cm^{-3}}$ density and
$10\;\mathrm{K}$ gas in an ambient medium of $0.5\;\mathrm{cm^{-3}}$ at
$1000\:\mathrm{K}$.  This gives roughly the same amount of mass enclosed within
the hot bubble at $30\:\mathrm{Myr}$.  The first contains a single spherical
clump with a radius of $0.2\;\mathrm{kpc}$.  The second contains the same amount
of cold mass spread over 6 clumps arranged at the center of each face of a cube
$0.2\;\mathrm{kpc}$ surrounding the star.  We use this idealized clumpy medium
to test the sensitivity of the model to small scale structure that may be
unresolved in lower resolution simulations. Figure~\ref{onestar_clumpyslice1}
shows a slice showing SPH particles at $50\;\mathrm{Myr}$ for the two clumpy
cases.

@@

We used the standard {\sc GASOLINE} star-formation recipe, based on the
algorithm proposed by \citet{Katz1992} and detailed further in
\citet{Stinson2006}.  We use a density threshold for star formation $n_{SF}$
shown in table 1 along with a temperature threshold of $T < 10^4\;\mathrm{K}$.
Thus, for a given eligible gas particle, the probability of forming a star each
timestep $P_{SF} = 1-\exp{-0.05\ \Delta t\over t_{\rm ff}}$, depends only on the
free-fall time $t_{\rm ff}$.  This corresponds to the effective star formation
density rate of $\dot \rho_* = 0.05\ \frac{\rho_{gas}}{t_{\rm ff}}$.  We also
include UV heating for $z=0$ \citep[as in][]{Shen2010} and a pressure floor that
ensures gas does not collapse beyond the resolvable Jeans length
\citep{Machacek2001}.

We also simulated these initial conditions using the established `blastwave'
feedback model from \citep{Stinson2006}, which has been a standard feedback
model for galaxy simulations in numerous previous studies.
\begin{table}
    \begin{tabular}{ c c c c c}
        \hline
        Simulation & $M_{tot} \mathrm{(M_\odot)}$ & $M_{gas} \mathrm{(M_\odot)}$
        & $\epsilon \mathrm{(pc)}$ & $n_{SF} \mathrm{cm^{-3}}$\\
        \hline
        Milky Way & $1.3\times10^{12}$ & $8.6\times10^9$ & 20  & $>10$\\
        Dwarf & $1.3\times10^{10}$ &  $8.6\times10^7$ & 4.3 & $>50$\\
    \end{tabular}
    \caption[Isolated Disc Initial Conditions]{Disc galaxy initial conditions.  $\epsilon$ is the gravitational
    softening and $n_{SF}$ is the star formation threshold.}
\end{table}

\subsubsection{ISM properties and Star Formation Rates}\label{ISM1}
\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/milkyway_outflow.eps}
    \caption[Outflow evolution in isolated Milky Way]{Outflow evolution for the
    Milky Way-like simulation.  The left hand plot shows the star formation rate
    and the outflow rate The right hand plot shows the average outflow
    velocity.}
    \label{milkyway_outflow1}
\end{figure*}

@@

Figure~\ref{disc_phase1} shows phase diagrams from both Milky Way and dwarf
galaxies.  Figure~\ref{milkyway_column1} shows column density and temperature for
the Milky Way, and figure~\ref{milkyway_outflow1} shows star formation rates and
outflow properties.  figures~\ref{dwarf_column1}~and~\ref{dwarf_outflow1} show the
same for the dwarf galaxy.  The Kennicutt-Schmidt relation for both galaxies is
shown in figure~\ref{kennicutt_schmidt1}.  The star formation and outflow properties are
discussed in section~\ref{Morphology1}.  Finally, we show some properties of the
multiphase particles in figure~\ref{multiphase_properties1}.

@@

Figure~\ref{multiphase_properties1} shows the that all particles stay in
the multiphase state as well as the maximum height reached by multiphase
particles.  The top figure shows that the vast majority of particles in either
the dwarf or the Milky Way convert back to single phase within
$10\;\mathrm{Myr}$.  The mean multiphase lifetime for the Milky Way was
$6.6\;\mathrm{Myr}$, and $2.7\;\mathrm{Myr}$ for the dwarf, well within the
range we should expect.  The reason for the shorter multiphase lifetimes in the
dwarf galaxy is simply the better mass resolution: the hot bubble interior
becomes resolved earlier in the dwarf than in the Milky Way.  Fewer than 0.5 per
cent of multiphase particles ever stay in the multiphase state for more than
$50\;\mathrm{Myr}$ in both the Milky Way and the dwarf.  The bottom figure
shows, again as we should expect, that most multiphase particles convert back to
single phase before they reach 1 scale height.  The mean maximum height for
multiphase particles was roughly $1/2$ a scale height for both simulations,
$0.51\;\mathrm{kpc}$ and $0.13\;\mathrm{kpc}$ for the Milky Way and dwarf
respectively.  Neither simulation had any multiphase particles reaching heights
of more than $10\;\mathrm{kpc}$ before converting back to single phase.  This
shows that multiphase particles are essentially embedded within the thin disc of
the ISM: all of the mass outflowing is fully-resolved hot gas, and its behaviour
is fully governed by standard hydrodynamics.  The winds driven from both
galaxies are ejected through nothing more than simple buoyancy.

>>>>

Another approach has been to explicitly model the multiphase ISM
below the resolution limit.  \citet{Springel2003} described a multiphase
model based on the theoretical framework of \citet{McKee1977}.  Each
particle was composed of an isobaric mix of cold clouds and ambient warm
to hot gas.  Radiative cooling converts warmer gas into cold.  The cold
phase forms stars on a characteristic timescale chosen to yield a
Schmidt-type star formation law.  An empirical model of stellar feedback
evaporates the cold phase.  \citet{Springel2003} recognized that while
this model works well for simulating star formation and feedback in
quiescent galaxies, the coupling of hot and cold mass can prevent hot
gas from leaving the disc as winds or outflows.  Their solution was to
convert a fraction of the feedback energy in a kinetic kick on selected
particles, in the same vein as \citet{Mihos1994}.

@@

Young stellar populations steadily release energy in the form of winds and SNe at
a rate of $3\times 10^{38}\;\mathrm{erg\; s^{-1} M_\odot^{-1}}$ for around 40
Myr~\citep{Leitherer1999}. We deposit this energy into the gas particle nearest
to the star particle.  In following with past work, we use the feedback rates
and times for supernovae, but the method is general enough to handle heating
from stellar winds, ionization, etc.  Heating takes effect
$4\;\mathrm{Myr}$ after a star forms, and continues until $30\;\mathrm{Myr}$
after the star particle forms (the time associated with SNII from OB stars).  Thus,
each supernova releases $10^{51}\;\mathrm{erg}$, and each star particle will
release $10^{49}\;\mathrm{erg M^{-1}_\odot}$ using the \citet{Chabrier2003} IMF.

\subsection{Thermal Conduction}
In an ionized gas, thermal conduction, mediated by electrons,
transports heat down temperature gradients.  This flux, $\mathbf{Q} =
-\kappa\nabla T$, depends on the temperature gradient and the conduction
coefficient, as derived by \citet{Cowie1977},
\begin{equation} \label{coefficient1}
    \kappa(T) = 1.8\left(\frac{2}{\pi}\right)^{3/2}\frac{T^{5/2}k_B^{7/2}}{m_e\,e^4\ln\Lambda}.
\end{equation}
This coefficient depends only on the Coulomb logarithm $\ln\Lambda$ (which has
an extremely weak dependence on density), and is well approximated by $\kappa(T)
= \kappa_0\,T^{5/2}$, where $\kappa_0$ is $6.1\times10^{-7}\;\mathrm{erg\;s^{-1}
K^{-7/2}cm^{-1}}$ in the absence of magnetic fields.  This drives a
corresponding mass flux, {\it in the opposite direction}.  With spherical
symmetry, this implies a mass flow rate that depends on the sound speed in the
hot gas, $c_{\rm s}$, as follows,
\begin{equation}\label{conservation1}
    \frac{5}{2}\dot M c_{\rm s}^2 = 4\,\pi^2r^2\kappa(T)\frac{{\rm d}T}{{\rm d}r}.
\end{equation}

These rates hold only when the mean free path of electrons in the medium is
smaller than the scale length of the temperature gradient.  If the gradient
becomes steep enough, the heat flux (and corresponding mass flux) saturates at a
value that depends only on the density, temperature, and thermal velocity of the
electrons in the medium \citep{Cowie1977},
\begin{equation}\label{heatflux1}
    \mathbf{Q} = \nabla\left(\frac{3}{2}n_ek_BT_ev_e\right).
\end{equation}
This saturation has the convenient numerical side effect of setting the smallest
timestep required to resolve this mass flux to $\sim 1/17$ the standard Courant
time, $t_C = \Delta x /c_s$.

@@

\subsection{Evaporation}
The dominant physical process governing mass flux between the hot and cold
phases of a feedback bubble is thermal conduction between the dense shell and
the hot interior.   As this process takes place on length scales far below the
resolution limit, we must capture its effects in a subgrid model.  For the thin
shell surrounding a feedback bubble, thermal conduction causes an evaporative
mass flux from the cold shell into the hot bubble.  Following
\citet{MacLow1988}, the mass flux into a bubble with interior temperature $T$
is,
\begin{equation}\label{massflux1}
    \frac{{\rm d }M_b}{{\rm d}t} = \frac{4\,\pi\mu}{25k_B}\kappa_0\,\frac{\Delta T^{5/2}}{\Delta x}\ A,
\end{equation}
where $A$ is the bubble surface area and $\Delta x$ is the thickness of the hot
layer ($\Delta x = R$ for spherical symmetry).  For the Smoothed Particle
Hydrodynamics (SPH) method used for our tests, we calculate evaporation using
the outer layer of hot particles bordering the cold gas.  The members of this
layer are those with no other hot particles within $45^o$ of the vector to the
centre of mass of their cold neighbours.  As we cannot directly determine the
radius of a well-resolved superbubble without expensive non-local calculations,
we need a way to allow each particle to estimate the radius and thus its
fractional contribution of the shell surface area.  The total area estimated by
all hot particles in a bubble should approach $\sim 4\pi R^2$ where $R$ is the
bubble radius.  For a poorly resolved bubble $R \sim 1-2\,h$, where $h$ is a hot
particle's SPH smoothing length.  For larger bubbles each hot particle
contributes an area of $\sim h^2$ and each particle sees a nearly plane-parallel
section of the cold shell.  We examined a number of bubbles at different stages
of growth, as well as a plane-parallel slab, and empirically found that a good
per-particle area estimate was $A = \frac{6\,\pi\,h^2}{N_{\rm hot}}$, where
$N_{\rm hot}$ is the number of hot neighbours for that particle and $\Delta x =
h$.  We stress that this is a fit for our specific SPH neighbour approach
(described below) that should be recalibrated for other codes.

@@

\begin{equation}\label{multiphase_fractions1}
    m = m_{\rm hot}+m_{\rm cold}
\end{equation}
\begin{equation}
    E = u_{\rm hot}m_{\rm hot}+u_{\rm cold}m_{\rm cold}
\end{equation}

Assuming pressure equilibrium, both phases will have the same pressure $P$, and
their densities are found using this and the total density $\rho$:
\begin{equation}\label{multiphase_pressurebalance1}
    \frac{P}{\rho} = \frac{(\gamma-1)E}{m}
\end{equation}
\begin{equation}\label{multiphase_densities1}
    \rho_{\rm cold} = \frac{P}{(\gamma-1)u_{\rm cold}}
\end{equation}
\begin{equation}
    \rho_{\rm hot} = \frac{P}{(\gamma-1)u_{\rm hot}}
\end{equation}

@@

We placed a star cluster with mass $3\times10^4\;\mathrm{M_\odot}$ in a uniform
periodic box $2\times2\times2\;\mathrm{kpc}$ in size, containing
$10^3\;\mathrm{K}$ gas with solar metallicity at a density of
$1\;\mathrm{cm^{-3}}$.   This gives a gas particle mass of $760\; M_\odot$,
$6080\; M_\odot$, and $48640\; M_\odot$ for resolutions of $128^3$, $64^3$, and
$32^3$ respectively.  These tests do not include photoheating.

Figure~\ref{onestar_column1} shows the column density projection for the three
different feedback models in an isotropic medium.  The hot interior of the
bubble produced using the simple feedback model contains less mass at $128^3$
than the direct injection model and is subsequently too poorly resolved for the
instabilities formed in the accelerated shell \citep{Vishniac1983} to mix the
bubble and shell through turbulence and diffusion.

@@

\subsubsection{Clumpy Medium}\label{clumpy1}
As the real ISM is highly inhomogeneous (and as \citet{Silich1996} showed, cold
clumps can also be a source of evaporated cold material), we ran two additional
simulations with cold, dense clumps with $100\;\mathrm{cm^{-3}}$ density and
$10\;\mathrm{K}$ gas in an ambient medium of $0.5\;\mathrm{cm^{-3}}$ at
$1000\:\mathrm{K}$.  This gives roughly the same amount of mass enclosed within
the hot bubble at $30\:\mathrm{Myr}$.  The first contains a single spherical
clump with a radius of $0.2\;\mathrm{kpc}$.  The second contains the same amount
of cold mass spread over 6 clumps arranged at the center of each face of a cube
$0.2\;\mathrm{kpc}$ surrounding the star.  We use this idealized clumpy medium
to test the sensitivity of the model to small scale structure that may be
unresolved in lower resolution simulations. Figure~\ref{onestar_clumpyslice1}
shows a slice showing SPH particles at $50\;\mathrm{Myr}$ for the two clumpy
cases.

@@

We used the standard {\sc GASOLINE} star-formation recipe, based on the
algorithm proposed by \citet{Katz1992} and detailed further in
\citet{Stinson2006}.  We use a density threshold for star formation $n_{SF}$
shown in table 1 along with a temperature threshold of $T < 10^4\;\mathrm{K}$.
Thus, for a given eligible gas particle($n>n_{SF}$ and $T<T_{SF}$, the
probability of forming a star each timestep $P_{SF} = 1-\exp{-0.05\ \Delta
t\over t_{\rm ff}}$, depends only on the free-fall time $t_{\rm ff}$.  This
corresponds to the effective star formation density rate of $\dot \rho_* = 0.05\
\frac{\rho_{gas}}{t_{\rm ff}}$.  We also include UV heating for $z=0$ \citep[as
in][]{Shen2010} and a pressure floor that ensures gas does not collapse beyond
the resolvable Jeans length \citep{Machacek2001}.

We also simulated these initial conditions using the established `blastwave'
feedback model from \citet{Stinson2006}, which has been a standard feedback
model for galaxy simulations in numerous previous studies.
\begin{table}
    \begin{tabular}{ c c c c c}
        \hline
        Simulation & $M_{tot} \mathrm{(M_\odot)}$ & $M_{gas} \mathrm{(M_\odot)}$
        & $\epsilon \mathrm{(pc)}$ & $n_{SF} \mathrm{cm^{-3}}$\\
        \hline
        Milky Way & $1.3\times10^{12}$ & $8.6\times10^9$ & 20  & $>10$\\
        Dwarf & $1.3\times10^{10}$ &  $8.6\times10^7$ & 4.3 & $>50$\\
    \end{tabular}
    \caption[Isolated Disc Initial Conditions]{Disc galaxy initial conditions.  $\epsilon$ is the gravitational
    softening and $n_{SF}$ is the star formation density threshold, above which
    stars are allowed to form.}
\end{table}

\subsubsection{ISM properties and Star Formation Rates}\label{ISM1}
\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/milkyway_outflow.eps}
    \caption[Outflow evolution in isolated Milky Way]{Outflow evolution for the
    Milky Way-like simulation.  The left hand plot shows the star formation rate
    and the outflow rate. The right hand plot shows the average outflow
    velocity.}
    \label{milkyway_outflow1}
\end{figure*}

@@

Figure~\ref{disc_phase1} shows phase diagrams from both Milky Way and dwarf
galaxies.  Figure~\ref{milkyway_column1} shows column density and temperature for
the Milky Way, and figure~\ref{milkyway_outflow1} shows star formation rates and
outflow properties.  Figures~\ref{dwarf_column1}~and~\ref{dwarf_outflow1} show the
same for the dwarf galaxy.  The Kennicutt-Schmidt relation for both galaxies is
shown in figure~\ref{kennicutt_schmidt1}.  The star formation and outflow properties are
discussed in section~\ref{Morphology1}.  Finally, we show some properties of the
multiphase particles in figure~\ref{multiphase_properties1}.

@@

Figure~\ref{multiphase_properties1} shows the duration that all particles stay in
the multiphase state as well as the maximum height reached by multiphase
particles.  The top figure shows that the vast majority of particles in either
the dwarf or the Milky Way convert back to single phase within
$10\;\mathrm{Myr}$.  The mean multiphase lifetime for the Milky Way was
$6.6\;\mathrm{Myr}$, and $2.7\;\mathrm{Myr}$ for the dwarf, well within the
range we should expect.  The reason for the shorter multiphase lifetimes in the
dwarf galaxy is simply the better mass resolution: the hot bubble interior
becomes resolved earlier in the dwarf than in the Milky Way.  Fewer than 0.5 per
cent of multiphase particles ever stay in the multiphase state for more than
$50\;\mathrm{Myr}$ in both the Milky Way and the dwarf.  The bottom figure
shows, again as we should expect, that most multiphase particles convert back to
single phase before they reach 1 scale height.  The mean maximum height for
multiphase particles was roughly $1/2$ a scale height for both simulations,
$0.51\;\mathrm{kpc}$ and $0.13\;\mathrm{kpc}$ for the Milky Way and dwarf
respectively.  Neither simulation had any multiphase particles reaching heights
of more than $10\;\mathrm{kpc}$ before converting back to single phase.  This
shows that multiphase particles are essentially embedded within the thin disc of
the ISM: all of the mass outflowing is fully-resolved hot gas, and its behaviour
is fully governed by standard hydrodynamics.  The winds driven from both
galaxies are ejected through nothing more than simple buoyancy.
